The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
references

The relation between UV luminosity and Star Formation Rate
\citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

@@

We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
\citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is quite similar to the 
Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
\citep{riebe13}.

@@

The halo abundance matching technique has been widely used \citep{colin99, kravtsov04}
resulting in good reproduction of the observed galaxy clustering. \citep{conroy06, lee09}. 
Here we use the simplest case with few premises: 
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable; the mass of
the DMH in which is located. This function must be monotone, this guarantees that most 
massive halos will host the most luminous galaxies in the same volume.
\end{enumerate}

@@

The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
 four parameter model:
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.

@@

The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a UV color to 
study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
This index appears when a power law fitting is performed over the spectral flux $f$ 
as function of the wavelength $\lambda$;
\[ f \propto \lambda^\beta.\]
The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
\begin{equation}
A_{1600} = 4.43 + 1.99 \beta,
\end{equation}
with $A_{1600}$ in magnitude units.

@@

\citet{bouwens12b} uses the fluxes on different bands to estimate $\beta$ on each LBG 
candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
between $\beta$ and the UV magnitude:
\begin{equation}
\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
                                   + \beta_{M_{UV}=-19.5}
\end{equation}
with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.

\citet{smit12} used the aforementioned relations to infer the corrected luminosity functions,
i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.

@@

Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

@@

A better model is a four parameter function. Each galaxy has a luminosity given
by:
  \begin{equation}
  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.

There are more complex models\citep{lee09} that includes a random behavior:
galaxies has not synchronization on the beginning of star forming stage, also
this stage may be time limited. This is called duty cycle. It is probable to
have in the observations some invisible galaxies in the UV continuum due their
duty cycle may has not started as well it may ended. Also may be present a
normal distribution of the luminosity around the expected values.

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_w_dust.pdf}
\caption{Individual small-box parameter estimation with dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_wo_dust.pdf}
\caption{Individual small-box parameter estimation with no-dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
 attenuation model.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
 attenuation model.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{graph_SFR_DMHM_w}
\end{figure}

>>>>

The relation between UV luminosity and Star Formation Rate
\citep{Madau98,Kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

@@

We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
\citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is quite similar to the 
Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
\citep{Riebe13}.

@@

The halo abundance matching technique has been widely used \citep{Colin99, Kravtsov04}
resulting in good reproduction of the observed galaxy clustering. \citep{Conroy06, Lee09}. 
Here we use the simplest case with few premises: 
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable; the mass of
the DMH in which is located. This function must be monotone, this guarantees that most 
massive halos will host the most luminous galaxies in the same volume.
\end{enumerate}

@@

The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
 four parameter model:
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenBosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{Moster10}.

@@

The UV Spectral Slope $\beta$ was introduced by \citet{Meurer99} as a UV color to 
study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
This index appears when a power law fitting is performed over the spectral flux $f$ 
as function of the wavelength $\lambda$;
\[ f \propto \lambda^\beta.\]
The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
\begin{equation}
A_{1600} = 4.43 + 1.99 \beta,
\end{equation}
with $A_{1600}$ in magnitude units.

@@

\citet{Bouwens12} uses the fluxes on different bands to estimate $\beta$ on each LBG 
candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
between $\beta$ and the UV magnitude:
\begin{equation}
\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
                                   + \beta_{M_{UV}=-19.5}
\end{equation}
with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.

\citet{Smit12} used the aforementioned relations to infer the corrected luminosity functions,
i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.

@@

Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{Madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{Kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{Madau98} and \cite{Kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

@@

A better model is a four parameter function. Each galaxy has a luminosity given
by:
  \begin{equation}
  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenBosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \cite{Moster10}.

There are more complex models\citep{Lee09} that includes a random behavior:
galaxies has not synchronization on the beginning of star forming stage, also
this stage may be time limited. This is called duty cycle. It is probable to
have in the observations some invisible galaxies in the UV continuum due their
duty cycle may has not started as well it may ended. Also may be present a
normal distribution of the luminosity around the expected values.

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_w_dust.pdf}
\caption{Individual small-box parameter estimation with dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{fig:OD1_individual_box_results_w}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_wo_dust.pdf}
\caption{Individual small-box parameter estimation with no-dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{fig:OD1_individual_box_results_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
 attenuation model.}
\label{fig:OD1_CosmicVar2_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
 attenuation model.}
\label{fig:OD1_CosmicVar2_wo_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{graph_SFR_DMHM_w}
\end{figure}
